---
output:
  github_document:
    html_preview: false
params:
  user: NULL
  user.twitter: NULL
  user.linkedin: "pauljhoffman"
  stats.private: TRUE
  stats.icons: TRUE
  langs.layout: "compact"
  recent.n: 10
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
args <- params
if (is.null(x = args[["user"]])) {
  args$user <- basename(path = getwd())
}
shields <- "https://img.shields.io/badge"
```

```{r packages, include=FALSE}
library(httr)
library(jsonlite)
```

```{r functions, include=FALSE}
#' Allowed Events
#'
#' Is a GitHub event allowed in the recent activity section. Allowed events
#' fall into one of the following categories
#' \itemize{
#'  \item \dQuote{IssuesEvent}
#  \item \dQuote{IssueCommentEvent}
#'  \item \dQuote{PullRequestEvent}
#' }
#'
#' @param e An event entry from the GitHub JSON
#'
#' @return \code{TRUE} if the event is allowed, otherwise \code{FALSE}
#'
AllowedEvent <- function(e) {
    events.allowed <- c(
    "IssuesEvent",
    # "IssueCommentEvent",
    "PullRequestEvent",
    "ReleaseEvent"
  )
  return(e$type %in% events.allowed)
}

#' Capitalize A String
#'
#' @param x A \code{\link[base]{character}} vector
#'
#' @return \code{x} with the first letter capitalized
#'
Cap <- function(x) {
  x <- paste(x, collapse = " ")
  if (nchar(x = x) == 1) {
    return(toupper(x = x))
  }
  return(paste0(
    toupper(x = substr(x = x, start = 1, stop = 1)),
    substr(x = x, start = 2, stop = nchar(x = x))
  ))
}

#' Build a Markdown Link
#'
#' @inheritParams Cap
#'
#' @return A \code{\link[base]{character}} vector with a markdown-style link
#' where \code{msg} points to \code{link}
#'
MDLink <- function(msg, link) {
  return(paste0("[", msg, "](", link, ")"))
}

#' Format Event Logs
#'
#' @inheritParams AllowedEvent
#'
#' @return \code{IssueLink}: The URL to GitHub issue
#'
#' @name FormatEvent
#' @rdname FormatEvent
#'
#' @return \code{IssueEvent}: A character string with the formatted issue event
#'
IssueEvent <- function(e) {
  return(paste(
    Cap(x = e$payload$action),
    MDLink(
      msg = paste(e$repo$name, e$payload$issue$number, sep = "#"),
      link = e$payload$issue$html_url
    )
  ))
}

#' @name FormatEvent
#' @rdname FormatEvent
#'
#' @return \code{IssueCommentEvent}: A character string with the formatted
#' comment event
#'
IssueCommentEvent <- function(e) {
  return(paste(
    "Commented on",
    MDLink(
      msg = paste(e$repo$name, e$payload$issue$number, sep = "#"),
      link = e$payload$comment$html_url
    )
  ))
}

#' @name FormatEvent
#' @rdname FormatEvent
#'
#' @return \code{PullRequestEvent}: A character string with the formatted pull
#' request event
#'
PullRequestEvent <- function(e) {
  action <- e$payload$action
  action <- switch(
    EXPR = action,
    "closed" = ifelse(
      test = e$payload$pull_request$merged,
      yes = "Merged",
      no = "Closed"
    ),
    Cap(x = action)
  )
  return(paste(
    action,
    MDLink(
      msg = paste(e$repo$name, e$payload$pull_request$number, sep = "#"),
      link = e$payload$pull_request$html_url
    )
  ))
}

#' @name FormatEvent
#' @rdname FormatEvent
#'
#' @return \code{ReleaseEvent}: A character string with the formatted release
#' event
#'
ReleaseEvent <- function(e) {
  return(paste(
    Cap(x = e$payload$action),
    MDLink(
      msg = paste(e$repo$name, e$payload$release$tag_name),
      link = e$payload$release$html_url
    )
  ))
}
```

# Hello World

I am Paul Hoffman, a senior bioinformatician with the [Satija](https://satijalab.org) and [Lappalainen](https://tllab.org) Labs at the New York Genome Center. My work revolves around building software and for bioinformatic analyses, including an [R package](https://github.com/satijalab/seurat) for analyzing single-cell data, along with several [extension](https://github.com/satijalab/seurat-data) [packages](https://github.com/mojaveazure/seurat-disk), and a [pipeline](https://github.com/LappalainenLab/RNApipeline) for processing RNA-seq data. I work primarily in R and Python, but am always learning.

## Social

<!-- badges: start -->
```{r social.badges, echo=FALSE, results="asis"}
social.base <- list(
  Twitter = list(alt = "Follow on Twitter", base = "https://twitter.com"),
  LinkedIn = list(
    alt = "Connect on LinkedIn",
    base = "https://www.linkedin.com/in"
  )
)
social.badges <- vector(mode = "character", length = length(x = social.base))
for (i in seq_along(along.with = social.base)) {
  social <- names(x = social.base)[i]
  key <- paste0("user.", tolower(x = social))
  if (is.null(x = args[[key]])) {
    next
  }
  social.badges[[i]] <- paste0(
    "[![",
    social.base[[social]]$alt,
    "](",
    paste0(
      shields,
      "/--",
      tolower(x = social),
      "?label=",
      social,
      "&logo=",
      social,
      "&style=social"
    ),
    ")](",
    paste(social.base[[social]]$base, args[[key]], sep = "/"),
    ")"
  )
}
cat(Filter(f = nchar, x = social.badges), sep = "\n")
```

<!-- badges: end -->

## Technologies Used

<!-- badges: start -->
![](https://img.shields.io/badge/r-%23276DC3.svg?&logo=r&logoColor=white)
![](https://img.shields.io/badge/python%20-%2314354C.svg?&logo=python&logoColor=white)
![](https://img.shields.io/badge/markdown-%23000000.svg?&logo=markdown&logoColor=white)
![](https://img.shields.io/badge/git%20-%23F05033.svg?&logo=git&logoColor=white)
![](https://img.shields.io/badge/github%20-%23121011.svg?&logo=github&logoColor=white)
![](https://img.shields.io/badge/docker%20-%230db7ed.svg?&logo=docker&logoColor=white)
<!-- ![](https://img.shields.io/badge/Google%20Cloud%20-%234285F4.svg?&logo=google-cloud&logoColor=white) -->
<!-- badges: end -->

## Basic Stats

```{r build.urls, echo=FALSE, results="hide"}
stats.gh <- "https://github.com/anuraghazra/github-readme-stats"
stats.base <- "https://github-readme-stats.vercel.app/api"
stats.url <- paste0(
  stats.base,
  "?username=",
  args$user,
  "&count_private=",
  tolower(x = args$stats.private),
  "&show_icons=",
  tolower(x = args$stats.icons)
)
langs.url <- paste0(
  stats.base,
  "/top-langs",
  "?username=",
  args$user,
  ifelse(
    test = is.null(x = args$langs.layout),
    yes = "",
    no = paste0("&layout=", args$langs.layout)
  )
)
```

<a href="`r stats.gh`">
  <img align="center" src="`r stats.url`" alt="GitHub stats" />
</a>
<a href="`r stats.gh`">
  <img align="center" src="`r langs.url`" alt= "Top languages" />
</a>

## Recent Activity

```{r recent.activity, echo=FALSE, results="asis"}
events.url <- paste(
  "https://api.github.com/users",
  args$user,
  "events/public",
  sep = "/"
)
response <- GET(url = events.url)
if (!identical(x = status_code(x = response), y = 200L)) {
  cat("No recent activity found")
} else {
  events <- fromJSON(txt = as.character(x = response), simplifyVector = FALSE)
  events <- Filter(f = AllowedEvent, x = events)
  page <- 2L
  while (length(x = events) < args$recent.n) {
    response <- GET(url = paste0(events.url, "?page=", page))
    if (!identical(x = status_code(x = response), y = 200L)) {
      break
    }
    resp.e <- fromJSON(txt = as.character(x = response), simplifyVector = FALSE)
    resp.e <- Filter(f = AllowedEvent, x = resp.e)
    events <- append(x = events, values = resp.e)
    page <- page + 1L
  }
}
events <- head(x = events, n = args$recent.n)
event.msgs <- vector(mode = "character", length = length(x = events))
for (i in seq_along(along.with = events)) {
  e <- events[[i]]
  event.msgs[[i]] <- switch(
    EXPR = e$type,
    "IssuesEvent" = IssueEvent(e = e),
    "IssueCommentEvent" = IssueCommentEvent(e = e),
    "PullRequestEvent" = PullRequestEvent(e = e),
    "ReleaseEvent" = ReleaseEvent(e = e)
  )
}
event.msgs <- paste(" -", event.msgs)
cat(event.msgs, sep = "\n")
```
