---
output: 
  github_document:
    html_preview: false
params:
  user: NULL
  user.twitter: NULL
  user.linkedin: "pauljhoffman"
  stats.private: TRUE
  stats.icons: TRUE
  langs.layout: "compact"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
args <- params
if (is.null(x = args$user)) {
  args$user <- basename(path = getwd())
}
shields <- "https://img.shields.io/badge"
```

```{r packages, echo=FALSE, results="hide"}
if (!requireNamespace("httr", quietly = TRUE)) {
  tryCatch(
    expr = install.packages("httr"),
    error = function(...) {
      stop("Cannot find or install httr", call. = FALSE)
    }
  )
}
library(httr)
```

# Hello World

I am Paul Hoffman, a senior bioinformatician wtih the [Satija](https://satijalab.org) and [Lappalainen](https://tllab.org) Labs at the New York Genome Center. My work revolves around building software and for bioinformatic analyses, including an [R package](https://github.com/satijalab/seurat) for analyzing single-cell data, along with several [extension](https://github.com/satijalab/seurat-data) [packages](https://github.com/mojaveazure/seurat-disk), and a [pipeline](https://github.com/LappalainenLab/RNApipeline) for processing RNA-seq data. I work primarily in R and Python, but am always learning.

## Social

<!-- badges: start -->
```{r social.badges, echo=FALSE, results="asis"}
social.base <- list(
  Twitter = list(alt = "Follow on Twitter", base = "https://twitter.com"),
  LinkedIn = list(
    alt = "Connect on LinkedIn",
    base = "https://www.linkedin.com/in"
  )
)
social.badges <- vector(mode = "character", length = length(x = social.base))
for (i in seq_along(along.with = social.base)) {
  social <- names(x = social.base)[i]
  key <- paste0("user.", tolower(x = social))
  if (is.null(x = args[[key]])) {
    next
  }
  social.badges[[i]] <- paste0(
    "[![",
    social.base[[social]]$alt,
    "](",
    modify_url(
      url = shields,
      path = paste(basename(path = shields), paste0("--", tolower(x = social)), sep  = "/"),
      query = list(
        label = social,
        logo = social,
        style = "social"
      )
    ),
    ")](",
    paste(social.base[[social]]$base, args[[key]], sep = "/"),
    ")"
  )
}
cat(Filter(f = nchar, x = social.badges), sep = "\n")
```

<!-- badges: end -->

## Technologies Used

<!-- badges: start -->
![](https://img.shields.io/badge/r-%23276DC3.svg?&logo=r&logoColor=white)
![](https://img.shields.io/badge/python%20-%2314354C.svg?&logo=python&logoColor=white)
![](https://img.shields.io/badge/markdown-%23000000.svg?&logo=markdown&logoColor=white)
![](https://img.shields.io/badge/git%20-%23F05033.svg?&logo=git&logoColor=white)
![](https://img.shields.io/badge/github%20-%23121011.svg?&logo=github&logoColor=white)
![](https://img.shields.io/badge/docker%20-%230db7ed.svg?&logo=docker&logoColor=white)
<!-- ![](https://img.shields.io/badge/Google%20Cloud%20-%234285F4.svg?&logo=google-cloud&logoColor=white) -->
<!-- badges: end -->

## Basic Stats

```{r build.urls, echo=FALSE, results="hide"}
stats.gh <- "https://github.com/anuraghazra/github-readme-stats"
stats.base <- "https://github-readme-stats.vercel.app/api"
stats.url <- modify_url(
  url = stats.base,
  query = list(
    username = args$user,
    count_private = tolower(x = args$stats.private),
    show_icons = tolower(x = args$stats.icons)
  )
)
langs.url <- modify_url(
  url = stats.base,
  path = file.path("api", "top-langs/"),
  query = list(
    username = args$user,
    layout = args$langs.layout
  )
)
"https://github-readme-stats.anuraghazra1.vercel.app/api/top-langs/?username=filiptronicek"
```

<a href="`r stats.gh`">
  <img align="center" src="`r stats.url`" />
</a>
<a href="`r stats.gh`">
  <img align="center" src="`r langs.url`" />
</a>

## Recent Activity

<!--START_SECTION:activity-->
